---
title: "iMIRAGE Vignette"
author: "Aritro Nath"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{iMIRAGE Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))


----

# Introduction 

The iMIRAGE package stands for imputed microRNA (miRNA) activity from gene expression. As the name suggests, the package imputes expression of miRNAs by constructing prediction models that only depend on the expression of levels of protein-coding genes (PCGs). In essence, iMIRAGE package can impute the miRNA profiles of samples where PCG expression data is availabe (for example, microarray or RNAseq) but do not contain miRNA expression. Using a *training* dataset containing both PCG and miRNA expression profiles, iMIRAGE trains prediction models using PCGs as features, and predicts miRNA expression in the dataset of interest. 

The iMIRAGE package also provides tools to create an integrated workflow, to clean-up, pre-process and harmonize the expression datasets. In addition, the package provides an option of using miRNA-target gene pair information to construct the prediction models 
